The Feasibility of Stylometry as a Service

### 2013-12-10 paper/paper.tex
Added paper to .gitignore and added listing package.

% Required Packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{url}

@@

@@

>>>>

% Required Packages
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{verbatim} % used to display code
\usepackage{hyperref}
%\usepackage{fullpage}
\usepackage[ansinew]{inputenc} % german umlauts
\usepackage[usenames,dvipsnames]{color}
\usepackage{float}
\usepackage{subfig}
\usepackage{tikz}
\usetikzlibrary{calc,through,backgrounds}
\usepackage{fancyvrb}
\usepackage{acronym}
\usepackage{amsthm} % Uuhhh yet another package
\VerbatimFootnotes % Required, otherwise verbatim does not work in footnotes!
%\usepackage{listings}

\definecolor{Brown}{cmyk}{0,0.81,1,0.60}
\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.9}

@@

\lstset{
language=bash,                          % Code langugage
basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
commentstyle=\color{gray},              % Comments font
numbers=left,                           % Line nums position
numberstyle=\tiny,                      % Line-numbers fonts
stepnumber=1,                           % Step between two line-numbers
numbersep=5pt,                          % How far are line-numbers from code
backgroundcolor=\color{lightlightgray}, % Choose background color
frame=none,                             % A frame around the code
tabsize=2,                              % Default tab size
captionpos=b,                           % Caption-position = bottom
breaklines=true,                        % Automatic line breaking?
breakatwhitespace=false,                % Automatic breaks only at whitespace?
showspaces=false,                       % Dont make spaces visible
showtabs=false,                         % Dont make tabls visible
columns=flexible,                       % Column format
morekeywords={__global__, __device__},  % CUDA specific keywords
}

@@

\section{Deployment}

The web application can be deployed via the following commands on a
Ubuntu 12.04 desktop installation:

\begin{lstlisting}[caption={Install Dependencies},label={lst:install}]
sudo apt-get update
sudo apt-get install ubuntu-desktop ant openjdk-7-jdk postgresql git
sudo add-apt-repository ppa:chris-lea/node.js
sudo apt-get update
sudo apt-get install nodejs
git clone https://github.com/LRParser/anonymouth.git
\end{lstlisting}

\begin{lstlisting}[caption={Start Service},label={lst:start}]
cd anonymouth
./bootstrap.sh
\end{lstlisting}
